---
title: "R Notebook"
output: html_notebook
---

# Part 2


#Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

1. Describe the data and the problem
# Hapiness is important because it's extremely vital to out own goals in life and can help us achieve many other cherished personal ambitions and goals. Also, by being happy, we have the potantial to change many other lives just by being ourselves. I went to hiking trip last week and we talked about the measurements in happiness on our way back home. Some people say people who'd rather die at their 80s are happier than those who want to die at their 40s (life expentancy) and some people have other paramters for happiness. I think it might be interesting and meaningful to dive into some data to dig out what really matters towards happiness. In this project, I use the data from The World Happiness Report, a landmark survey of the state of global happiness. The World Happiness 2017, which ranks 155 countries by their happiness levels, was released at the United Nations at an event celebrating International Day of Happiness on March 20th. Leading experts across fields – economics, psychology, survey analysis, national statistics, health, public policy and more – describe how measurements of well-being can be used effectively to assess the progress of nations. 

2. Read in and check data

# Load packages
```{r}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(dplyr)
library(formattable)
library(plotly)
library(countrycode)
library(maps)
```

# Read data
```{r}
X2016 <- read_csv("~/Desktop/projects/dsi-principles-prog/midterm/2016.csv")
X2017 <- read_csv("~/Desktop/projects/dsi-principles-prog/midterm/2017.csv")
nrow(X2017)
```


2. Clean up the data. 
```{r}
#Merge two datasets and mutate colomns
df1<- merge(X2016[,c(1,3,7,8,9)],
           X2017[,c(1,2,6,7,8)],
           by.x = "Country",
           by.y = "Country")
colnames(df1)<-c("Country","Happiness_Rank_2016","Happiness_Rank_2017","Economy_GDP_per_capita_2016","Economy_GDP_per_capita_2017","Family_2016","Family_2017","Health_2016","Health_2017")

columndif<- function(x,y){
  x-y 
}
df1 %>% 
  mutate(Happiness_Rank_Difference=columndif(Happiness_Rank_2017,Happiness_Rank_2016)) %>% 
  mutate(Economics_Difference=columndif(Economy_GDP_per_capita_2017,Economy_GDP_per_capita_2016)) %>% 
  mutate(Family_Difference=columndif(Family_2017,Family_2016)) %>% 
  mutate(Health_Difference=columndif(Health_2017,Health_2016)) %>% 
#filter(Country,Happiness_Rank_Difference,everything())
df1
```

```{r}
#form a data table 
formattable(df1,list(
  `Rank Change` = formatter(
    "span",
    style=~formattable::style(color=ifelse(`Rank Change`>0,"green","red"))))) %>%
    as.datatable()
```

# Add one column for cotinents. Would like to see the correlation between continents and hapiness. 
```{r}
continent <- function(country){ 
  Europe <- c("Norway", "Denmark", "Iceland", "Switzerland", "Finland","Netherlands", "Sweden", "Austria", "Ireland", "Germany","Belgium", "Luxembourg", "United Kingdom", "Czech Republic","Malta", "France", "Spain", "Slovakia", "Poland", "Italy","Russia", "Lithuania", "Latvia", "Moldova", "Romania","Slovenia", "North Cyprus", "Cyprus", "Estonia", "Belarus","Serbia", "Hungary", "Croatia", "Kosovo", "Montenegro","Greece", "Portugal", "Bosnia and Herzegovina", "Macedonia","Bulgaria", "Albania", "Ukraine")
  Australia <- c("New Zealand", "Australia")
  Asia <- c("Israel", "United Arab Emirates", "Singapore", "Thailand", "Taiwan Province of China","Qatar", "Saudi Arabia", "Kuwait", "Bahrain", "Malaysia", "Uzbekistan", "Japan","South Korea", "Turkmenistan", "Kazakhstan", "Turkey", "Hong Kong S.A.R., China", "Philippines","Jordan", "China", "Pakistan", "Indonesia", "Azerbaijan", "Lebanon", "Vietnam","Tajikistan", "Bhutan", "Kyrgyzstan", "Nepal", "Mongolia", "Palestinian Territories","Iran", "Bangladesh", "Myanmar", "Iraq", "Sri Lanka", "Armenia", "India", "Georgia", "Cambodia", "Afghanistan", "Yemen", "Syria")
  North_America <- c("Canada", "Costa Rica", "United States", "Mexico",  
"Panama","Trinidad and Tobago", "El Salvador", "Belize", "Guatemala","Jamaica", "Nicaragua", "Dominican Republic", "Honduras","Haiti")
  South_America <- c("Chile", "Brazil", "Argentina", "Uruguay","Colombia", "Ecuador", "Bolivia", "Peru","Paraguay", "Venezuela")
  
  ctnt <- case_when(country %in% Europe ~ "Europe",
                    country %in% Australia ~ "Australia",
                    country %in% Asia ~ "Asia",
                    country %in% North_America ~ "North_America",
                    country %in% South_America ~ "South_America")
  ctnt
}
```

```{r}
continent("Canada")
```

```{r}
df1 %>% 
  continent()

for (i in country) {

if (country == "Norway", "Denmark", "Iceland", "Switzerland", "Finland","Netherlands", "Sweden", "Austria", "Ireland", "Germany","Belgium", "Luxembourg", "United Kingdom", "Czech Republic","Malta", "France", "Spain", "Slovakia", "Poland", "Italy","Russia", "Lithuania", "Latvia", "Moldova", "Romania","Slovenia", "North Cyprus", "Cyprus", "Estonia", "Belarus","Serbia", "Hungary", "Croatia", "Kosovo", "Montenegro","Greece", "Portugal", "Bosnia and Herzegovina", "Macedonia","Bulgaria", "Albania", "Ukraine")
print Europe ;
  
else if (country == "New Zealand", "Australia")
print Australia;
   
else if {country == 
}   
  
} 
df1 %>%

mutate(continent=)
```

```{r}
df1 <- df1 %>% 
  select(Country,Continent, everything())

df1.Continent <- function(df1) { 
  select(-3) %>%
  group_by(Continent) %>%
  summarise_at(vars(-Country), function(mean(., na.rm=TRUE)))}
df1.Continent
```

```{r}
#Trying to find the correlation
Cor.data <- cor(df1[, Num.cols])
```


