---
title: "assign4"
output: html_notebook
---
```{r}
library(lubridate)
library(stringr)
library(readr)
library(RVerbalExpressions)
```


For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 

# Part 1

## R4DS 16.4.5

Create a vector of dates giving the first day of every month in the current year. 
```{r}
ymd("2019-01-01") + months(0:11)
floor_date(today(), unit = "year") + months(0:11) #another approach
```
Write a function that given your birthday (as a date), returns how old you are in years.
```{r}
age <-  function(bday) {
  (bday %--% today()) %/% years(1)
}
age(ymd('1996-10-30'))
```

Write a function that given your birthday, returns the day of the week you were born on. 

```{r}
week_bday <- function(bday){
  weekdays(ymd(bday))
}
week_bday("1996-10-30")
```

## R4DS 14.3.2.1

Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)
```{r}
str_view(stringr::words, ".......", match = TRUE)
```
```{r}
stringr::words
x <- rx_something() %>%
  rx_repeat_previous(7)
words[grepl(x, words)]
```


## R4DS 14.3.3.1

Use str_detect to find all words that:
That only contain consonants. (Hint: thinking about matching “not”-vowels.)
Empirically verify the rule “i before e except after c”.
Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.

```{r}

```{r}
words[str_detect(words, "^[^aeiou]+$") ]
consonants_only <- rx() %>%
  rx_start_of_line() %>%
  rx_something_but("aeiou") %>%
  rx_end_of_line()
consonants_only
words[str_detect(words, consonants_only) ]
```

```

```{r}
words[str_detect(words, "cie")]
nc_ie <- rx() %>%
  rx_find("cie")
nc_ie
words[str_detect(words, nc_ie)]
```



```{r}
telrx <- rx()  %>% 
  rx_start_of_line() %>% 
  rx_maybe("(") %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_maybe(")") %>% 
  rx_any_of(".-") %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of(".-") %>% 
  rx_digit() %>% 
  rx_repeat_previous(4) %>% 
  rx_end_of_line()
telrx
```

```{r}
tel_num_rv <- function(number){

telrx <- rx() %>% 
  rx_start_of_line() %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>%
  rx_digit() %>% 
  rx_repeat_previous(4) %>% 
  rx_end_of_line() %>% 
  grepl(number) %>% 
  print()
}
tel_num_rv(c("217-277-2867", "217.277.2867", "EM7.277.2867"))
```



